Stage IGE

### 2025-09-02 presentation/presentation_mf.qmd
Presentation MF

\fontsize{7}{7}\selectfont Station Météo-France de Saint-Marcel-lès-Valence, Vallée du Rhône ($M_1^\ast$, $M_1$, $M_3$)

![](../outputs/series/26313001_serie.png)

>>>>

\fontsize{7}{7}\selectfont Station Météo-France de Saint-Marcel-lès-Valence, Vallée du Rhône ($M_2$, $M_3$, $M_3$)

![](schema/26313001_serie_fev.png)

\fontsize{7}{7}\selectfont Station Météo-France de Saint-Marcel-lès-Valence, Vallée du Rhône ($M_1^\ast$, $M_2$, $M_2$)

![](schema/26313001_serie_nov.png)
